Mixture-of-interests models for representing users with diverse interests

### 2017-10-28 paper/paper.tex
Start plotting hyperparam search results.

\title{Parameter-efficient multi-modal embeddings for representing diverse user interests}
\author{Maciej Kula}
\email{maciej.kula@gmail.com}
\date{\today}
\settopmatter{printacmref=false, printccs=false, printfolios=true}
\setcopyright{none}
\acmConference[]{}{}{}

@@

\keywords{Recommender Systems, Matrix Factorization, Binary Representations}

\begin{abstract}
Most existing recommendation approaches implicitly treat user tastes as unimodal, resulting in an average-of-tastes representations when multiple distinct interests are present. We show that appropriately modelling the multi-faceted nature of user tastes through a mixture-of-tastes model leads to large increases in recommendation quality at a very modest cost in model complexity. Our result holds both for deep sequence-based and traditional factorization models. 
\end{abstract}

>>>>

\title{Mixture-of-interests models for representing users with diverse interests}
\author{Maciej Kula}
\email{maciej.kula@gmail.com}
\date{\today}
\settopmatter{printacmref=false, printccs=false, printfolios=true}
\setcopyright{none}
\acmConference[]{}{}{}

@@

\keywords{Recommender Systems, Matrix Factorization, Sequence-based Recommendations}

\begin{abstract}
Most existing recommendation approaches implicitly treat user tastes as unimodal, resulting in an average-of-tastes representations when multiple distinct interests are present. We show that appropriately modelling the multi-faceted nature of user tastes through a mixture-of-tastes model leads to large increases in recommendation quality at a modest cost in model complexity. Our result holds both for deep sequence-based and traditional factorization models. 
\end{abstract}
